Adaptive Waveform Inversion for Transmitted Wavefields

### 2024-07-23 repro/papers/awi/paper.tex
penalty stuff added

\section{Introduction}
Full waveform inversion (FWI) refers to the inference of mechanical
parameter distribution within a material object  (the earth, a human
body, a manufactured artifact,...) from the measurement of wave motion
at its surface. Over the last several decades, this task has come to
be carried out by minimizing the difference between computationa
prediction of wave measurement versus actual observed
measurements. The mechanical parameters to be inferred appear as
coefficients in systems of partial differential equations governing
the wave motion, and discrete representations of these parameters form
the unknown vectors in the optimization problems thus generated.

@@

While heuristic justifications for AWI (and
many details of implementation) are discussed in these and other
works, a clear explanation for its effectiveness is 
so far missing from the literature. In this short note, I show that
for active sensing of acoustic materials with unique arrival times of
transmitted waves
(that is, unique rays of geometric asymptotics between sources and
receivers), the AWI objective function is an approximation to the
mean-square time-of-travel misfit. Thus AWI and travel time fitting
lead to similar material parameter estimates. Since the latter is
widely believed to be a near-optimal method for wave velocity
estimation, this demonstration explains roughly ``why AWI works'', at
least within this restricted scope.

The reader will
note that a normalization component of the AWI objective function
definition is very
important in reaching this conclusion. The connection between
objective normalization and the close relation to travel time
inversion has nothing to do with
the reasons for normalizing the objective advanced in the
literature \cite[]{Warner:16,LiAlkhalifah:21}.

After establishing
the class of problems to be studied and notations for their
description in the following section, I present the asymptotic
analysis leading to the main conclusion in the next. The close relation
between AWI objective and travel time misfit no longer mecessarily
holds if multiple rays connect source and receiver. I discuss these
and other aspects of AWI and related approaches in a brief final section.

@@

Since linear acoustics is time-translation invariant, its solution commutes with time convolution, that is,
\[
 \bar{F}[m]\bar{w} = \bar{F}[m](u* w) = (F[m]w)*u
\]
Since the known source $w$ is not adjusted during the inversion, 
introduce the notation $S[m]$ for the convolution operator with kernel $F[m]w$:
\begin{equation}
  \label{eqn:sdef}
  (F[m]w)*u \equiv S[m]u
\end{equation}
\cite{Warner:16} assume (implicitly) that there is always an exact
solution of the extended inversion problem. That is, they assume that
for any $m$, there is an extended source $\bar{w}$, or equivalently an
adaptive filter $u[m;d]$ with $\bar{w}=w*u[m;d]$, for which
$S[m]u[m;d]= d$. [This proposition is dubious, but is easy to work
around, as will be seen below. Also, \cite{Warner:16} also formulate
AWI in terms of the inverse filter, that is, $u$ for which
$u*d = F[m]w$, and in fact recommend that definition. The present
discussion uses only the forward filter.] If
$\kappa = \kappa^*, \beta = \beta^*$, then $\bar{w}$ should be $= w$,
so the adaptive kernel $u[m;d]$ should be $=\delta(t)$ for all
${\bf x}_s,{\bf x}_r$. Such a kernel $u[m;d]$ is in the null space of
multiplication by $t$.

@@

Transient acoustic sources have no DC (zero frequency) component and
are relatively small at low frequencies. One way to enforce these
characteristics is to assume that the wavelet $w$ is the time
derivative of another wavelet $v$, also transient ($v(t;{\bf x}_s)=0$
for $|t| \gg 0$). Set $\lambda(w) = \|v\|/\|w\|$. $\lambda$ is a proxy for wavelength: it is the reciprocal of RMS frequency.

@@

Applying the approximation \ref{eqn:hadamard}, obtain
\begin{equation}
  \label{eqn:spwe}
S[m]u({\bf x}_r,t;{\bf x}_s) \approx a[m]({\bf x}_s,{\bf x}_r) (w*u)(t-\tau[m]({\bf x}_s,{\bf x}_r))
\end{equation}
Assume that the data is noise-free:
$$
d({\bf x}_r,t;{\bf x}_s)=(F[m^*]w) ({\bf x}_r,t;{\bf x}_s) \approx a[m^*]({\bf x}_s,{\bf x}_r) w(t-\tau[m^*]({\bf x}_s,{\bf x}_r))
$$
The (approximate) solution of $S[m]u[m;d]=d$ is obvious by inspection:
\begin{equation}
  \label{eqn:notl2}
  u[m;d]({\bf x}_r,t;{\bf x}_s) = \frac{a[m^*]({\bf x}_s,{\bf x}_r)}{a[m]({\bf x}_s,{\bf x}_r)}\delta(t-\tau[m^*]({\bf x}_s,{\bf x}_r)+\tau[m]({\bf x}_s,{\bf x}_r)).
\end{equation}
There is immediately a big problem: this $u[m;d]$ is not square-integrable, and the AWI objective $J_{\rm AWI}$ is undefined. To fix this, it's necessary to re-define $u[m;d]$ as the solution of a regularized least squares problem: define
\begin{equation}
  \label{eqn:reg}
  u[m;d] = \mbox{argmin}_u (\|S[m]u-d\|^2 + \sigma^2\|u\|^2)
\end{equation}
$$
\approx \mbox{argmin}_u (\|a[m](w*u)(\cdot-\tau[m])-a[m^*]w(\cdot-\tau[m^*])\|^2 + \sigma^2\|u\|^2)
$$

@@

With these conventions, re-write equation \ref{eqn:reg} in terms of the Fourier transforms $\hat{u}[m;d],\hat{w}$ of $u[m;d]$ and $w$:
\begin{equation}
  \label{eqn:freqreg}
\hat{u}[m;d] \approx \mbox{argmin}_{\hat{u}}\left(\int d\omega |a\hat{w}\hat{u}e^{i\omega \tau}-a^*\hat{w}e^{i\omega\tau^*}|^2 + \sigma^2 |\hat{u}|^2\right)
\end{equation}
The normal equation for the least squares problem \ref{eqn:freqreg} is
$$
(a^2 |\hat{w}|^2 +\sigma^2)\hat{u} = a a^*|\hat{w}|^2e^{i\omega(\tau^*-\tau)}
$$
the solution of which is
$$
\hat{u}[m;d] \approx \frac{a^*}{a}\hat{g}_{\frac{a^*}{a}\sigma} e^{i\omega(\tau^*-\tau)}
$$
where
$$ 
\hat{g}_{\sigma} = \frac{(a^*)^2|\hat{w}|^2}{(a^*)^2|\hat{w}|^2 + \sigma^2}.
$$
depends only the ``true'' model $m^*$. Transient acoustic sources are effectively bandlimited: $\hat{w}(\omega) \rightarrow 0$ faster than any negative power of $\omega$ as $|\omega| \rightarrow \infty$ and is analytic, whence $\hat{g}_{\sigma}:$ tends to $1$ almost everywhere as $\sigma \rightarrow 0$. Hence the inverse Fourier transform $g_{\sigma}$ tends to $\delta$ in the sense of distributions, and 
$$
u[m;d](t) \approx \frac{a^*}{a}g_{\frac{a^*}{a}\sigma}(t-(\tau^*-\tau))
$$
to a multiple of a shifted $\delta$, in fact exactly the distribution
solution of $\bar{S}[m,w]u=d$ given in equation \ref{eqn:notl2}. However for $\sigma>0$, $u[m;d]$ is square integrable.

\cite{HuangSymes2015SEG} presented an analysis of the Matched Source
Waveform Inversion (MSWI) objective function, which is essentially the
numerator of the right hand side in the definition
\ref{eqn:tJz} of the AWI objective. This analysis was based in turn on ideas presented in Song's thesis
\cite[]{Song:94c}. MSWI deals with the extended source $\bar{w}$, but
the same construction applies to the adptive filter $u$. With $u$ replaced by $u[m;d]$,  this MSWI objective is
\[
J_{\rm MSWI}[m;d] = \int dt |tu[m;d]|^2 \approx \frac{(a^*)^2}{a^2} \int dt\, t^2|g_{\frac{a^*}{a}\sigma}(t-(\tau^*-\tau))|^2
\]
\[
=\frac{(a^*)^2}{a^2} \int dt\, (t+(\tau^*-\tau))^2|g_{\frac{a^*}{a}\sigma}(t)|^2
\]
\begin{equation}
  \label{eqn:MSWI}
  =\frac{(a^*)^2}{a^2} \int dt\, (t^2 + 2t
  (\tau^*-\tau)+(\tau^*-\tau)^2)|g_{\frac{a^*}{a}\sigma}(t)|^2
\end{equation}
As noted by \cite{HuangSymes2015SEG}, the linear term (in t) on the
right-hand side of \ref{eqn:MSWI} vanishes,
since $g$ is necessarily even in time (since its Fourier transform is
real). So
\begin{equation}
  \label{eqn:MSWIasym}
  J_{\rm MSWI}[m;d] \approx
\frac{(a^*)^2}{a^2} \int dt\, t^2|g_{\frac{a^*}{a}\sigma}(t)|^2
+(\tau^*-\tau)^2\frac{(a^*)^2}{a^2}\|g_{\frac{a^*}{a}\sigma}\|^2
\end{equation}
The first term tends to zero as $\sigma \rightarrow 0$, since
$g_{\sigma}$ is a delta-family, so you can make it negligible with
proper choice of $\sigma$. The second term suggests that this function
is related to the travel-time error $\tau^*-\tau$.

The relation is obscured by the presence of of the amplitude ratio
$a^*/a$ both as a multiplier and in the scaling of $\sigma$. Since the
amplitudes depend on $m$, their presence may influence the location
(or even the presence) of stationary points of $J_{\rm MSWI}$ for
models differing in their travel time predictions. So stationary
points of the MSWI objective may not yield slowness models that match
travel-times with the data, even in the noise-free case (though
the examples reported by \cite{HuangSymes2015SEG, HuangSymes:Geo17}, and other works
cited there, suggest that sometimes this is the case).

Comparing the definitions \ref{eqn:tJz} of $J_{\rm AWI}$ and
\ref{eqn:MSWI} of $J_{\rm MSWI}$, ones sees
that the two functions differ only by the factor $\|u[m;d]\|^{-2}$ in
the former. Using the geometric asymptotics approximation, 
$$
\|u[m;d]\| \approx \frac{a^*}{a}\|g_{\frac{a^*}{a}\sigma}\| + O(\sigma^2)
$$
Therefore, multiplication of the MSWI objective by $\|u[m;d]\|^{-2}$
precisely removes the amplitude factor in the right-hand side of the
relation \ref{eqn:MSWIasym}. Restoring the source and receiver
coordinates to the notation,
$$
J_{\rm AWI}[m;d] \approx \sum_{{\bf x}_s,{\bf x}_r} (\tau[m^*]({\bf
  x}_s,{\bf x}_r)-\tau[m]({\bf x}_s,{\bf x}_r))^2 + O(\sigma^2)
$$
In other words, the AWI objective is {\em exactly} an approximation to
the travel-time tomography objective, with errors proportional to the
``wavelength'' $\lambda(w)$ and the regularization parameter
$\sigma^2$.

@@

@@

\section{Conclusion}
In this paper, I have shown that AWI is a good approximation to least
squares travel time inversion of transmitted wave data, up to errors proportional to a typical
data wavelength and to a regularization (``pre-whitening'')
weight. However, the argument leading to this conclusion works only if
the material model is assumed slowly varying so that geometric
acoustics accurately describes the solution of the wave equation, and if
sources and receivers are sufficiently close to one another to be
connected by unique rays. The first condition may be ignored to some
extend - the conclusion of this paper likely holds if the data is
dominated by ballistic transmitted waves. However the second condition
is essential: in the presence of multiple arrivals, the connection
with travel time inversion breaks down, and AWI and similar algorithms
become essentially as prone to cycle-skipping as is FWI.

>>>>

\section{Introduction}
Full waveform inversion (FWI) refers to the inference of mechanical
parameter distribution within a material object  (the earth, a human
body, a manufactured artifact,...) from the measurement of wave motion
at its surface. Over the last several decades, this task has come to
be carried out by minimizing a measure of the difference between computational
prediction of wave data versus actual observed
data. The mechanical parameters to be inferred appear as
coefficients in systems of partial differential equations governing
the wave motion, and discrete representations of these parameters form
the unknown vectors in the optimization problems thus generated.

@@

While these and other works discuss heuristic justifications for AWI and
many details of implementation, a clear explanation for its effectiveness is 
so far missing from the literature. In this short note, I show that
for active sensing of acoustic materials with unique arrival times of
transmitted waves
(that is, unique rays of geometric asymptotics between sources and
receivers), the AWI objective function is an asymptotic (in time
frequency) approximation to the
mean-square time-of-travel misfit. Thus AWI and travel time fitting
lead to similar material parameter estimates. Since the latter is
widely believed to be a near-optimal method for wave velocity
estimation, this demonstration explains roughly ``why AWI works'', at
least within this restricted scope.

The reader will
note that a normalization component of the AWI objective function
definition is 
important in reaching this conclusion. The connection between
objective normalization and the asymptotic equivalence to travel time
inversion for transmission data has nothing to do with
the reasons for normalizing the objective previoiusly advanced in the
literature \cite[]{Warner:16,LiAlkhalifah:21}. Another modification of
FWI based on similar ideas, Matched Source Waveform Inversion (MSWI)
(\cite{HuangSymes2015SEG,HuangSymes:Geo17}) lacks the AWI normalization,
and has a looser relation to travel time inversion. The arguments
presented here for AWI (and MSWI) are refinements of those given by
\cite{HuangSymes:Geo17}. which were in turn based on ideas presented in Song's thesis
\cite[]{Song:94c}.

After establishing the class of problems to be studied and notations
for their description in the following section, I present the
asymptotic analysis leading to the main conclusion in the next. In
effect, AWI regularizes or relaxes the FWI problem. For many inverse
problems, regularization has been accomplished via additive penalty
functions. In section four, I explain the relation between AWI and a
penalty formulation of the wave inverse problem. The
close relation between AWI objective and travel time misfit is limited
in scope: in the fifth section, I show that it does not hold in
general for transmitted wave data in which multiple rays connect
source and receiver.

The analysis explained here sheds no light on the effectiveness of AWI
for reflected wave data, and the approach has so far been limited
inversion of data modeled by acoustic wave propagation. I discuss
these and other aspects of AWI and related approaches in a brief final
section.

@@

Since linear acoustics is time-translation invariant, its solution commutes with time convolution, that is,
\[
 \bar{F}[m]\bar{w} = \bar{F}[m](u* w) = (F[m]w)*u
\]
Since the known source $w$ is not adjusted during the inversion, 
introduce the notation $S[m]$ for the convolution operator with kernel $F[m]w$:
\begin{equation}
  \label{eqn:sdef}
  (F[m]w)*u \equiv S[m]u
\end{equation}
\cite{Warner:16} assume (implicitly) that there is always an exact
solution of the extended inversion problem. That is, they assume that
for any $m$, there is an extended source $\bar{w}$, or equivalently an
adaptive filter $u[m;d]$ with $\bar{w}=w*u[m;d]$, for which
$S[m]u[m;d]= d$. This proposition is dubious, but is easy to work
around, as will be seen below. Also, \cite{Warner:16} also formulate
AWI in terms of the inverse filter, that is, $u$ for which
$u*d = F[m]w$, and in fact recommend that definition. The present
discussion uses only the forward filter.

If $\kappa = \kappa^*, \beta = \beta^*$, then $\bar{w}$ should be $= w$,
so the adaptive kernel $u[m;d]$ should be $=\delta(t)$ for all
${\bf x}_s,{\bf x}_r$. Such a kernel $u[m;d]$ is in the null space of
multiplication by $t$.

@@

Transient acoustic sources have no DC (zero frequency) component and
are relatively small at low frequencies. One way to enforce these
characteristics is to assume that the wavelet $w$ is the time
derivative of another wavelet $v$, also transient ($v(t;{\bf x}_s)=0$
for $|t| \gg 0$). Set $\lambda(w) = \|v\|/\|w\|$. $\lambda$ is a proxy
for wavelength: it is the reciprocal of RMS frequency of $v$.

@@

Applying the approximation \ref{eqn:hadamard}, obtain
\begin{equation}
  \label{eqn:spwe}
S[m]u({\bf x}_r,t;{\bf x}_s) \approx a[m]({\bf x}_s,{\bf x}_r) (w*u)(t-\tau[m]({\bf x}_s,{\bf x}_r))
\end{equation}
Assume that the data is noise-free:
$$
d({\bf x}_r,t;{\bf x}_s)=(F[m^*]w) ({\bf x}_r,t;{\bf x}_s) \approx a[m^*]({\bf x}_s,{\bf x}_r) w(t-\tau[m^*]({\bf x}_s,{\bf x}_r))
$$
The (approximate) solution of $S[m]u[m;d]=d$ is obvious by inspection:
\begin{equation}
  \label{eqn:notl2}
  u[m;d]({\bf x}_r,t;{\bf x}_s) = \frac{a[m^*]({\bf x}_s,{\bf x}_r)}{a[m]({\bf x}_s,{\bf x}_r)}\delta(t-\tau[m^*]({\bf x}_s,{\bf x}_r)+\tau[m]({\bf x}_s,{\bf x}_r)).
\end{equation}
There is immediately a big problem: this $u[m;d]$ is not
square-integrable, and the AWI objective $J_{\rm AWI}$ is
undefined. To fix this, it's necessary to replace $u[m;d]$ by
$u_{0,\sigma}[m;d]$,  the solution of a regularized least squares problem: 
\begin{equation}
  \label{eqn:reg}
  u_{0,\sigma}[m;d] = \mbox{argmin}_u (\|S[m]u-d\|^2 + \sigma^2\|u\|^2)
\end{equation}
$$
\approx \mbox{argmin}_u (\|a[m](w*u)(\cdot-\tau[m])-a[m^*]w(\cdot-\tau[m^*])\|^2 + \sigma^2\|u\|^2)
$$

@@

With these conventions, re-write equation \ref{eqn:reg} in terms of the Fourier transforms $\hat{u}[m;d],\hat{w}$ of $u_{0,\sigma}[m;d]$ and $w$:
\begin{equation}
  \label{eqn:freqreg}
\hat{u}[m;d] \approx \mbox{argmin}_{\hat{u}}\left(\int d\omega |a\hat{w}\hat{u}e^{i\omega \tau}-a^*\hat{w}e^{i\omega\tau^*}|^2 + \sigma^2 |\hat{u}|^2\right)
\end{equation}
The normal equation for the least squares problem \ref{eqn:freqreg} is
\[
(a^2 |\hat{w}|^2 +\sigma^2)\hat{u} = a a^*|\hat{w}|^2e^{i\omega(\tau^*-\tau)}
\]
the solution of which is
\[
\hat{u}[m;d] \approx \frac{a^*}{a}\hat{g}_{\frac{\sigma}{a}} e^{i\omega(\tau^*-\tau)}
\]
where
$$ 
\hat{g}_{\sigma} = \frac{|\hat{w}|^2}{|\hat{w}|^2 + \sigma^2}.
$$
Transient acoustic sources are effectively bandlimited:
$\hat{w}(\omega) \rightarrow 0$ faster than any negative power of
$\omega$ as $|\omega| \rightarrow \infty$ and is entire analytic, whence $\hat{g}_{\sigma}:$ tends to $1$ almost everywhere as $\sigma \rightarrow 0$. Hence the inverse Fourier transform $g_{\sigma}$ tends to $\delta$ in the sense of distributions, and 
$$
u_{0,\sigma}[m;d](t) \approx \frac{a^*}{a}g_{\frac{\sigma}{a}}(t-(\tau^*-\tau))
$$
to a multiple of a shifted $\delta$, in fact exactly the distribution
solution of $\bar{S}[m,w]u=d$ given in equation \ref{eqn:notl2}. However for $\sigma>0$, $u_{0,\sigma}[m;d]$ is square integrable.

\cite{HuangSymes2015SEG} presented an analysis of the Matched Source
Waveform Inversion (MSWI) objective function, which is essentially the
numerator of the right hand side in the definition
\ref{eqn:tJz} of the AWI objective. This analysis was based in turn on ideas presented in Song's thesis
\cite[]{Song:94c}. MSWI deals with the extended source $\bar{w}$, but
the same construction applies to the adaptive filter $u$. With $u$ replaced by $u_{0,\sigma}[m;d]$,  the MSWI objective is
\[
J_{\rm MSWI}[m;d] = \int dt |tu_{0,\sigma}[m;d]|^2 \approx \frac{(a^*)^2}{a^2} \int dt\, t^2|g_{\frac{\sigma}{a}}(t-(\tau^*-\tau))|^2
\]
\[
=\frac{(a^*)^2}{a^2} \int dt\, (t+(\tau^*-\tau))^2|g_{\frac{\sigma}{a}}(t)|^2
\]
\begin{equation}
  \label{eqn:MSWI}
  =\frac{(a^*)^2}{a^2} \int dt\, (t^2 + 2t
  (\tau^*-\tau)+(\tau^*-\tau)^2)|g_{\frac{\sigma}{a}}(t)|^2
\end{equation}
As noted by \cite{HuangSymes2015SEG}, the linear term (in t) on the
right-hand side of \ref{eqn:MSWI} vanishes,
since $g$ is necessarily even in time (since its Fourier transform is
real). So
\begin{equation}
  \label{eqn:MSWIasym}
  J_{\rm MSWI}[m;d] \approx
\frac{(a^*)^2}{a^2} \int dt\, t^2|g_{\frac{\sigma}{a}}(t)|^2
+(\tau^*-\tau)^2\frac{(a^*)^2}{a^2}\|g_{\frac{\sigma}{a}}\|^2
\end{equation}
The first term tends to zero as $\sigma \rightarrow 0$, since
$g_{\sigma}$ is a delta-family, so you can make it negligible with
proper choice of $\sigma$. The second term suggests that this function
is related to the travel-time error $\tau^*-\tau$.

The relation is obscured by the presence of of the amplitudes
$a^*, a$ both in the multiplier and in the scaling of $\sigma$. Since the
amplitudes depend on $m$, their presence may influence the location
(or even the presence) of stationary points of $J_{\rm MSWI}$ for
models differing in their travel time predictions. So stationary
points of the MSWI objective may not yield slowness models that match
travel-times with the data, even in the noise-free case (though
the examples reported by \cite{HuangSymes2015SEG, HuangSymes:Geo17}, and other works
cited there, suggest that sometimes this is the case).

Comparing the definitions \ref{eqn:tJz} of $J_{\rm AWI}$ and
\ref{eqn:MSWI} of $J_{\rm MSWI}$, ones sees
that the two functions differ only by the factor $\|u_{0,\sigma}[m;d]\|^{-2}$ in
the former. Using the geometric asymptotics approximation, 
$$
\|u_{0,\sigma}[m;d]\| \approx \frac{a^*}{a}\|g_{\frac{\sigma}{a}}\| + O(\sigma^2)
$$
Therefore, multiplication of the MSWI objective by $\|u_{0,\sigma}[m;d]\|^{-2}$
precisely removes the amplitude factor in the right-hand side of the
relation \ref{eqn:MSWIasym}. Restoring the source and receiver
coordinates to the notation,
$$
J_{\rm AWI}[m;d] \approx \sum_{{\bf x}_s,{\bf x}_r} (\tau[m^*]({\bf
  x}_s,{\bf x}_r)-\tau[m]({\bf x}_s,{\bf x}_r))^2 + O(\sigma^2)
$$
In other words, the AWI objective is {\em exactly} an approximation to
the travel-time tomography objective, with errors proportional to the
``wavelength'' $\lambda(w)$ and the regularization parameter
$\sigma^2$.

@@

\section{Relation to Penalty Formulation}
Penalty functions provide a means to convert naively posed
inverse problems into well-posed problems, with solutions that exist
and depend stably on proper data. The ``pre-whitening'' construction
explained in the last section is a classic example, adding a scaled
mean-square of the adaptive filter to the residual mean-square to
produce an objective with a square-integrable (finite-energy)
minimizer. This penalty construction if often called {\em Tihonov
  regularization}. The MSWI and AWI objective functions have a deeper
relation to a penalty construction, however: they are
suitably defined limits of penalty functions.

This relation is abstract, and does not just pertain to the problems
discussed in this paper. To derive this abstract relation, suppose for
the moment that $S:U \rightarrow D$ is a bounded and coercive from a
domain Hilbert space $U$ to a range Hilbert space $D$. That is, for
real numbers $0 < C_* \le C^*$,
\[
  C_*\|u\|_U \le \|Su\|_D \le C^*\|u\|
\]
Suppose that $d \in D$ (``data''), and $T$ is another bounded operator $U \rightarrow E$, $E$
another Hilbert space. Define
\begin{equation}
  \label{eqn:eq1}
  J_{\alpha}(u) = \frac{1}{2}(\|Su-d\|_D + \alpha^2\|Tu\|_E^2).
\end{equation}
and
\begin{equation}
  \label{eqn:eq0}
  \tJa= \min_u J_{\alpha}(u) = J_{\alpha}(u_{\alpha})
\end{equation}
Since $S$ is coercive, the minimum is well-defined for any
$\alpha \ge 0$, and the minimizer $\ua \in U$ satisfies the normal
equation
\begin{equation}
  \label{eqn:eq0n}
  (S^TS + \alpha^2 T^TT) \ua = S^Td
\end{equation}

The claim to be established is that
\begin{equation}
  \label{eqn:eq4}
  \lim_{\alpha \rightarrow 0} \frac{1}{\alpha^2}  (\tJa-\tJz).= \frac{1}{2}\|T\uz\|^2
\end{equation}

To see this, use the normal equation to write
\[
  \ua = (S^TS + \alpha^2 T^TT)^{-1}T^Td = (S^TS + \alpha^2 T^TT)^{-1}S^TS \uz
\]
\begin{equation}
  \label{eqn:eq2}
  = \uz - \alpha^2 (S^TS + \alpha^2 T^TT)^{-1}T^TT\uz = \uz-\alpha^2 \va
\end{equation}
Note that $\va = (S^TS + \alpha^2 T^TT)^{-1}T^TT\uz$ is uniformly bounded in $\alpha \ge 0$.

Substitute the RHS of equation \ref{eqn:eq2} into the definition \ref{eqn:eq1} to obtain
\begin{equation}
  \label{eqn:eq3}
  \tJa = \frac{1}{2}(\|S\uz-d\|_d^2 - 2 \alpha^2\langle S\uz-d, S\va\rangle_d + \alpha^2\|T\uz\|_m^2 + O(\alpha^4))
\end{equation}
The second term on the RHS of equation \ref{eqn:eq3} vanishes thanks to the normal equation, and the first term is precisely $\tJz$. The conclusion \ref{eqn:eq4} follows.

To apply the assertion \ref{eqn:eq4} to the MSWI objective, make the
following choices, for each $m$ in the domain of $F$: $S$ is the regularized
modeling operator $(S[m],\sigma I)^T$.  Its domain is $U=L^2(\bR)$, of
which $u$ (the adaptive filter) is a member, and 
its range is $D = L^2(\bR) \oplus
L^2(\bR)$. The role of $d$ is played  the
augmented data $(d,0)^T$. $T$ is a modified multiply-by-$t$ operator
$Tu(t)=\max(|t|, t_{\rm max}) \mbox{sgn}(t)u(t)$, with domain $U$ and
range $E=L^2(\bR)$. The truncation by $t_{\rm max} > 0$ is necessary
to make $T$ bounded, but can be chosen large enough relative to the
support of the filter (necessarily bounded in practical calculation)
to have no effect. Then $\Ja$ becomes $J_{{\rm MSWI},\alpha,\sigma}[m,u;d]$, where
\begin{equation}
  \label{eqn:eq5}
   J_{{\rm MSWI},\alpha,\sigma}[m,u;d] = \frac{1}{2}\left(\|S[m]u-d\|^2 +
   \sigma^2\|u\|^2 + \alpha^2\|Tu\|^2\right)
 \end{equation}
The minimizer $\ua$ over $u$ of $ J_{{\rm MSWI}, \alpha,\sigma}[m,u;d]$ is
$u_{{\rm MSWI},\alpha,\sigma}[m;d]$, and $\tJa$ becomes
\begin{equation}
  \label{eqn:eq6}
  \tilde{J}_{{\rm MSWI},\alpha,\sigma}[m;d] =
  J_{{\rm MSWI},\alpha,\sigma}[m,u_{{\rm MSWI},\alpha,\sigma}[m;d];d].
\end{equation}
Note that $u_0$ becomes $u_{0,\sigma}[m;d]$, and $\tilde{J}_0$ becomes
$\tilde{J}_{0,\sigma}[m;d]$ which means exactly what
it did in the previous section. The subscript ${\rm MSWI}$ is left
off for $\alpha=0$, for reasons that will become apparent shortly.

With these correspondences, equation \ref{eqn:eq4} becomes
\begin{equation}
  \label{eq7}
  \lim_{\alpha \rightarrow 0}
  \frac{1}{\alpha^2}\left(\tilde{J}_{{\rm MSWI},\alpha,\sigma}[m;d]-\tilde{J}_{0,\sigma}[m;d]\right)=
  J_{\rm MSWI}[m;d]
\end{equation}

To derive the analogous relation for AWI only requires re-definition
of the operator $T$: it becomes (taking explicitly into account
dependence on source and receiver coordinates)
\begin{equation}
  \label{eqn:eq8}
  T[m;d] u(\bx_r,t;\bx_s) = \frac{\max(|t|, t_{\rm max})
    \mbox{sgn}(t)}{\|u_{0,\sigma}[m;d](\bx_r,\cdot;\bx_s)\|}
  u(\bx_r,t;\bx_s).
\end{equation}
That is, for AWI, $T$ depends on both model and data. Define
\begin{equation}
  \label{eqn:eq5a}
   J_{{\rm AWI},\alpha,\sigma}[m,u;d] = \frac{1}{2}\left(\|S[m]u-d\|^2 +
   \sigma^2\|u\|^2 + \alpha^2\|T[m;d]u\|^2\right)
 \end{equation}
The minimizer $\ua$ over $u$ of $ J_{{\rm AWI}, \alpha,\sigma}[m,u;d]$ is
$u_{{\rm AWI},\alpha,\sigma}[m;d]$, and $\tJa$ becomes
\begin{equation}
  \label{eqn:eq6a}
  \tilde{J}_{{\rm AWI},\alpha,\sigma}[m;d] =
  J_{{\rm AWI};\alpha,\sigma}[m,u_{{\rm AWI};\alpha,\sigma}[m;d];d].
\end{equation}
Note that the definitions \ref{eqn:eq5} and \ref{eqn:eq6} are exactly
the same as the corresponding definition \ref{eqn:eq5a} and
\ref{eqn:eq6a} when $\sigma=0$, which is why the subscripts ${\rm
  MSWI}$ and ${\rm AWI}$ are left off in these cases.

Precisely the
same reasoning then leads to
\begin{equation}
  \label{eq9}
  \lim_{\alpha \rightarrow 0}
  \frac{1}{\alpha^2}\left(\tilde{J}_{{\rm AWI},\alpha,\sigma}[m;d]-\tilde{J}_{0,\sigma}[m;d]\right)=
  J_{\rm AWI}[m;d]
\end{equation}

@@

\section{Conclusion}
In this paper, I have shown that AWI is a good approximation to least
squares travel time inversion of transmitted wave data, up to errors proportional to a typical
data wavelength and to a regularization (``pre-whitening'')
weight. However, the argument leading to this conclusion works only if
the material model is assumed slowly varying so that geometric
acoustics accurately describes the solution of the wave equation, and if
sources and receivers are sufficiently close to one another to be
connected by unique rays. The first condition may be ignored to some
extent - the conclusion of this paper likely holds if the data is
dominated by ballistic transmitted waves. The second condition
is essential: even for purely transmitted waves, the presence of
multiple arrivals breaks the connection
with travel time inversion, and AWI and similar algorithms
become essentially as prone to cycle-skipping as is FWI.

The analysis presented here has nothing to say about AWI applied to
reflected wave data. \cite{Warner:16} and others have
suggested that AWI is effective in that context. If so, the underlying
mechanism remains to be explained.
